What do incoming university students believe about open science practices in

### 2021-09-10 analysis/Manuscript.Rmd

---
title: What do incoming university students believe about open science practices in
  psychology?
author:
- name: Jennifer L. Beaudry
  affiliation: '1'
  corresponding: yes
  address: Postal address
  email: jbeaudry@swin.edu.au
  role: null
- name: Michael C. Philipp
  affiliation: '2'
  role: null
- name: Matt N. Williams
  affiliation: '2'
  role: null
shorttitle: Psychology students' beliefs about open science
output:
  papaja::apa6_word: default
  papaja::apa6_pdf: default
authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
  Enter author note here.
abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  One or two sentences to put the results into a more **general context**.
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  <!-- https://tinyurl.com/ybremelq -->
keywords: open science, psychology, teaching, reproducibility, replication
wordcount: X
bibliography: ['r-references.bib','Undergrads & Open Science (public).bib']
floatsintext: yes
figurelist: no
tablelist: no
footnotelist: no
linenumbers: yes
mask: yes
draft: no
documentclass: apa6
classoption: man
affiliation:
- id: '1'
  institution: Swinburne University of Technology
- id: '2'
  institution: Massey University
---
<!-- I've only partially entered authorship deets for the moment and set it to mask authorship info when knitting
It's set to default to knit to .docx, but can also knit to pdf (if you have a tex distro installed)
The pdf looks nicer and might be good for a preprint but .docx probably easiest to use for journal submissions.
To knit to RMarkdown you will probably need the papaja package installed, and to knit to .pdf you will need a tex distro (e.g., TinyTex).
However, it is possible to run all the R code (without knitting to .docx or .pdf) by clicking Run > Run All Chunks Below.
This could be useful in future for readers interested in reproducing results but who don't have or wish to install 
papaja and its many dependencies.
-->

@@

```{r setup, include = FALSE}
library(papaja) #install with devtools1
library(here)
library(tidyverse)
library(finalfit) # to keep trailing zeros & round_tidy
library(psych) #for correlation matrices
library(tidyselect) 
library(psychometric) # for correlation confidence intervals - might not need...
library(broom)

@@

The last decade has seen unprecedented change in methodological and reporting practices in psychology. These changes were partly precipitated by what is popularly known as the "replication crisis": The discovery that close replications of published psychological studies are often unable to replicate the original findings [@kleinInvestigatingVariationReplicability2014; @kleinManyLabsInvestigating2018]. These apparent problems with replication have lead to a variety of potential solutions to make research practices more transparent, including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@simmons21WordSolution2012], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018]. These calls for more transparent research practices prompted the discipline to reflect on the norms and beliefs that underpin its practice of research. Many studies have polled researchers' understandings of and adherence to open science norms, beliefs, and practices [e.g., @baker500ScientistsLift2016; @openscienceworkinggroup2017SurveyOpen2018; @harrisUseReproducibleResearch2018]. In turn, initiatives have been directed toward training undergraduate students in the adoption of an open science ethos [e.g., @chopikHowWhetherTeach2018; @graheHarnessingUndiscoveredResource2012; @jekelHowTeachOpen2020; @schonbrodtTrainingStudentsOpen2019].  These initiatives help ingrain open science norms and change attitudes about research practices, but we know little about what these students know or believe about open science research practices prior to entering the university classroom.

The most comprehensive set of principles for how science *ought* to be practiced are Merton's norms of science [@mertonNoteScienceDemocracy1942]. Scientists [@Anderson2000] and graduate students [@andersonGraduateStudentExperience1994] alike have historically endorsed the normative value of Merton's principles. Furthermore, many of the recent practices designed to make science more transparent and open reflect Mertonian norms. For example, the practice of sharing open source software directly corresponds to the Mertonian norm of *communism*: Scientists should have common ownership of scientific goods. Similarly, the practices of sharing of preprints for open peer review and open data for checking of reproducibility corresponds to the norm of communality, but also to that of *organised skepticism*: Scientific claims should be subjected to critical scrutiny. Preregistration can be connected to the norm of *disinterestedness*: By making (and preregistering) decisions about how to analyse data before results are produced, a researcher can limit the degree to which the substantive results produced by different analytic strategies affect their decisions regarding which analyses to report. In this sense, the ongoing reform in psychological research can partly be understood as simultaneously a set of new practices and a re-affirmation of established norms.<!--Should we consider citing someone for these links? Personally I have seen Simine draw these parallels between norms and open science practices and would favour crediting her here, however I'm sure that others have made similar analyses and so would be happy to cite others or to see this as such a commonly held set of beliefs that no citations are required--->

Nevertheless, rapid changes in methodological practice and empirical findings present significant pedagogical challenges for the teacher of psychology. Keeping textbooks and other instructional materials up to date is difficult when supposedly well-established findings are contradicted by new replications emerging at a rapid pace. Furthermore, training in emerging methodological practices is crucial for graduate students who may go on to apply psychological research methods themselves, so that they may produce research that is even more replicable than that of previous generations. Even for students who do not go on to conduct research themselves, an understanding of contemporary methodological practices - and problems with methodological practices in psychology - is essential for becoming informed and critical consumers of psychological knowledge. However, how we best provide this understanding is no trivial task. Indeed, there are several reasons why it might be unwise to assume a simple knowledge deficit, where the teacher's only role is to dispense an understanding of open science and transparent research practices.

First, unlike some areas of psychology covered in undergraduate courses (e.g., models of working memory, or the internal workings of human senses), the replication crisis is frequently discussed in mainstream and social media [e.g., @ogradyPsychologyReplicationCrisis2020; @yongPsychologyReplicationCrisis2016; @yongPsychologyReplicationCrisis2018]. Many students may plausibly have some knowledge about these issues obtained prior to (or independently of) their formal studies. Teaching methods should thus be informed by some understanding of what students' pre-existing levels of knowledge are.

Second, when psychology students are beginning their university studies, they are often learning for the first time about how and why it is useful to apply scientific methods to studying human behaviour (rather than only relying on alternative sources of knowledge such as intuition or anecdote or authority). An over-emphasis on problems with replicability could leave these students unconvinced that scientific methods for studying human behaviour are valuable *at all*, leaving them to favour even less credible alternative sources of knowledge. For instance, @chopikHowWhetherTeach2018 found that undergraduate students tended to trust the results of psychological studies *less* after a one-hour educational lecture about the replication crisis 
^[1 Notably, the effect of the lecture on trust of psychological studies was relatively small (d = -.36), and mean trust levels remained fairly high after the lecture (M = 4.94 on a scale of 1 to 7).].

Third, anecdotal evidence suggests that students being taught about open science practices and reforms to improve reproducibility (such as open sharing of data and analysis code) are often surprised that this is not *already* standard practice [e.g. see tweets on this topic: @burak_tunca_uygun_tunc_2021; @duygu_uygun-tunc_uygun_tunc_last_2021; @lorne_campbell_distributary_academic_minzlicht_2018].<!--I'm not sure what happened to these citations but I can't find them in our library anymore - need to fix --> In other words, students' naive conception of how science works may, in some ways, be closer to that embodied in recent reforms rather than "business as usual" practices. Indeed, surveys of scientists' subscriptions to Mertonian norms have often found that while most scientists endorse Mertonian norms such as communality, universalism and disinterestedness, this is by no means the case for all scientists. Furthermore, they typically perceive the behaviour of other scientists as being less consistent with these norms than their own [@andersonNormativeDissonanceScience2007]. Therefore - for some students - teaching about reform may be less a matter of conveying new information and more one of reinforcing "naive" assumptions. In fact, although beyond the scope of this article, it is *possible* that incoming undergraduate students more strongly endorse open science norms than do academics.

<!-- I think it'd be useful here if we were able to point to examples of the anecdotal evidence mentioned above - anyone come across anything (even just on social media?) 
Also maybe add more about what we know about academics' endorsement of open science norms.
-->

These considerations suggest that it is important that teachers wishing to inform undergraduate psychology students about the replication crisis and open science practices have some understanding of what such students actually know and believe about these topics already. In addition, undergraduate psychology students themselves represent one of the most important audiences for psychological research: The number of undergraduate students enrolled in psychology courses in any given year dwarfs the number of academics working in psychology. As such, the *preferences* of these students with respect to reproducibility and open science practices are themselves important as a phenomenon of interest. If, for example, undergraduate psychology students have a strong preference that journal articles are freely available to members of the public, this preference on the part of some of the consumers of the knowledge we produce should have some bearing on our choices in relation to sharing of manuscripts. This is especially the case given that undergraduate students are directly or indirectly responsible for much of the funding which allows universities to operate and research to be conducted. In fact, in serving as participants for course credit in many universities, undergraduate psychology students also provide the data underlying much psychological research.

<!-- I'm not sure about the argument in the above paragraph - might be somewhat of a stretch? 
MP: Maybe a stretch, but given we have a good rationale already, it might be worth trying to keep it. We may need a reference to two to help make some of the claims more concrete though.-->

For these reasons, we aimed to conduct a study describing what incoming undergraduate students of psychology believe about reproducibility and open science practices in psychology. Our survey encompassed norms (how students felt research *should* be conducted), norms in practice (how students believe psychological research *is* conducted) and replicability (how replicable students believe psychological research is). In doing so we hope to provide knowledge which can inform the pedagogy of teaching about replication and open science practices. This study is exploratory [see @wagenmakersAgendaPurelyConfirmatory2012] and descriptive, and does not involve the specification or testing of hypotheses.

@@

Of the remaining `r n` participants, most reported that they were
18-24 years old (*n* = `r age[1,2]`), `r age [2,2]` 
reported that they were 25-34 years old, `r age [3,2]` were 35-44 years old,
`r age [4,2]` were 45-54 years old, and `r age [5,2]` was 55-64 years old.

The majority of participants (*n* = `r gender[1,2]`) reported that they were female, 
`r gender[2,2]` reported that they were male, `r gender[3,2]` participant reported 
their gender identity as "queer man", and `r gender[3,2]` participant reported 
non-binary gender.^[While the response "queer man" could potentially be coded as
"male", we are aware that some individuals who report gender in this way would
not feel that such reclassification was appropriate. We have retained the original
response in order to provide a faithful representation of the participant's 
self-reported gender.]

Nearly all reported that they graduated from high
school or secondary school (*n* = `r hs_status[3,2]`). Of those participants who 
attended high school, a little less than half completed psychology courses in 
high school (*n* = `r hs_psyc[2,2]`). In terms of their nationality, most 
participants reported that they were Australian (*n* = `r nationality[3,2]`), 
from the United Kingdom (*n* = `r nationality[24,2]`), or Chinese 
(*n* = `r nationality[6,2]`). In terms of where the participants were attending 
university, most reported that they were in Australia (*n* = `r uni_country[1,2]`), 
the United Kingdom (*n* = `r uni_country[5,2]`), or New Zealand (*n* = `r uni_country[4,2]`). About 2/3rds of participants reported that at least one of their parents attended university (*n* = `r first_gen[2,2]`). Students were recruited from nine universities, with the largest number of responses recorded from participants enrolled at the University of Queensland (*n* = `r nrow(filter(df, university_recoded == "University of Queensland"))`), University of Adelaide (*n* = `r nrow(filter(df, university_recoded == "University of Adelaide"))`), and the University of Bath (*n* = `r nrow(filter(df, university_recoded == "University of Bath"))`). While, the majority of participants (*n* = `r nrow(filter(df, degree_type == "Non-psychology"))`) indicated that they were enrolled in a non-psychology degree such as a Bachelor of Science or Bachelor of Arts (*n* = `r nrow(filter(df, degree_recoded == "Bachelor of Science"))`, *n* = `r nrow(filter(df, degree_recoded == "Bachelor of Arts"))` respectively), most were completing a psychology major (*n* = `r nrow(filter(df, major_recoded == "Psychology"))`).

@@

Our approach to measuring norms and counternorms focussed on participants' evaluation of ten specific open science practices that reflected diverse open science norms rather than trying to measure endorsement of the more abstract Mertonian norms (cf. Anderson et al., 2007). <!-- Mention here our discussions workshopping of common open science norms at SIPs? ! -->
The open science practices assessed in our survey included: critical thinking, preregistration, registered reports, p-hacking, hypothesising after the results are known (HARKing), providing sufficent information of replicability, preprints, open materials, open data, and open access publishing. Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." There were 20 scenarios in total (see Table \@ref(tab:norm_counternorm_items)). Participants rated their agreement with each prescriptive statement on a 1 (strongly disagree) to 5 (strongly agree) scale.

@@

We also sought to measure participants' normative beliefs about how psychological science was actually conducted by researchers around the world. To that end we asked participants, "When you consider all of the psychology studies conducted globally each year, what percentage of them would have the following characteristics?" The ten characteristics explicitly described each of the ten open science practices (see Table XX). Participants were given a slider bar ranging from 0% to 100% to record their estimate.

@@

In line with our preregisterd analysis plan, we calculated the difference in means
between responses to each norm item and its accompanying counternorm, along with 
95% confidence intervals. For this analysis, we removed three cases with missing values. 
Table XX displays the means and standard deviations for each norm, counternorm, 
and the difference values.

@@

In general, the students seemed to endorse open science practices: For seven of the ten open science practices, agreement with the norm item was stronger than for the corresponding counternorm. However, the extent to which participants endorsed open science norms varied very substantially across different practices. In terms of open science norms, participants most strongly endorsed the idea that researchers should provide sufficient information about studies to permit replicability, be critical of published findings, and avoid p-hacking (means > 4). They also tended to agree that researchers should avoid HARKing, share papers as open access, share open materials, and preregister their studies; the means for these items were all between 3.5 and 4 (4 representing 'agree'). On the other hand, they tended to disagree with the practice of sharing preprints prior to peer review, and to a lesser extent with sharing open data. The practice of registered reports was the one about which participants were most equivocal, with very similar levels of agreement (near the midpoint of 3) with both norm and counternorm for this item. This may be relatively unsurprising, given that the registered reports are perhaps the most recent innovation in the list of practices.

Unsurprisingly, there were fairly substantial negative correlations between the norm and counternorm pairs, although this was not the case for all pairs: For the norm and counternorm items relating to preregistrations, the correlation was `r sprintf('%.2f', cor(df$prereg_norm, df$prereg_cnorm))`. Similarly for the norm and counternorm items relating to HARKing, the correlation was negative but very small.

@@

# clean up the tibble                          
practice_means_corr <- practice_means_corr %>% 
  rename(Practice = practice) %>% 
  dplyr::select(-c(estimate, conf.low, conf.high)) %>% 
  relocate (Practice, .before = Norm) %>% 
  relocate (p.value, .after = last_col())

# breadcrumbs:
# need to figure out whether I can rotate a page in papaja
# I need to use apa_tables.... (in line with papaja)
# update practice descriptions so they make sense to readers

@@

## Norms in practice
Participants were also asked to estimate the proportion of psychology studies estimated globally which apply ten practices. These practices corresponded approximately to the ten norm-counternorm pairs, albeit with one norm excluded on the basis of not referring to behaviour (critically evaluating published studies vs. accepting them), and one practice added out of interest (data sharing on request). For many of these practices, participants estimates were near the midpoint of 50%. This said, participants perceived some practices as being applied relatively infrequently: For example, the mean estimate of the prevalence of HARKing, preprint sharing before publication, and open data sharing were all near 30%. Participants seemed to perceive that the most common practice was providing enough information in written reports to permit replication without asking any questions of the original researchers. It is perhaps fair to say that participants' mean estimate that `r paste(round(mean(df$detailed_methodology, na.rm = TRUE), 2), "%", sep = "")` of studies have this characteristic represents a rather optimistic projection.

```{r norms in practice}

# select columns that relate to norms in practice & pivot it long & drop the na values
in_prac_long <- df %>% 
  dplyr::select(c(id,preregistration:open_access)) %>% 
      pivot_longer (cols = -id,
                names_to = "practice",
                values_to = "prevalence rating") %>% 
  drop_na()

# get the n values for each of the practices
in_prac_counts <- in_prac_long %>% 
  dplyr::group_by(practice) %>% 
  count() %>% 
  ungroup()

# calculate means
in_prac_ms_sds <- in_prac_long %>%
  dplyr::group_by(practice) %>%
  summarise(mean = mean(`prevalence rating`),
            sd = sd(`prevalence rating`)) %>%
  ungroup()

# join the n values with the means
in_prac_means <- in_prac_counts %>% inner_join(in_prac_ms_sds)

# calculate 95% CIs
error <- qnorm(0.975) * in_prac_means$sd/sqrt(in_prac_means$n)
in_prac_means$lower <- in_prac_means$mean - error
in_prac_means$upper <- in_prac_means$mean + error

# combine means & SDs
in_prac_means$`Prevalence Ratings` <- paste0(round_tidy(in_prac_means$mean,2),
                          " (", 
                          round_tidy(in_prac_means$sd,2),
                            ")", 
                            " [",
                            round_tidy(in_prac_means$lower,2),
                            ", ", 
                            round_tidy(in_prac_means$upper,2),
                            "]")

# clean it up into a new dataframe with only the columns we need
in_practice_means <- in_prac_means %>% 
  dplyr::select(practice, `Prevalence Ratings`) %>% 
  rename(Practice = practice)

# breadcrumbs:
# I need to use apa_tables.... (in line with papaja)
# update practice descriptions so they make sense to readers

>>>>

---
title: What do incoming university students believe about open science practices in
  psychology?
author:
- name: Jennifer L. Beaudry
  affiliation: '1'
  corresponding: yes
  address: Postal address
  email: jbeaudry@swin.edu.au
  role: null
- name: Michael C. Philipp
  affiliation: '2'
  role: null
- name: Matt N. Williams
  affiliation: '2'
  role: null
shorttitle: Psychology students' beliefs about open science
output:
  papaja::apa6_word: default
  papaja::apa6_pdf: default
authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
  Enter author note here.

# Abstract: |

## BACKGROUND: Rapid changes to methodological best practices present significant challenges for educating students new to the field of psychology. Some students may have existing knowledge about recent methodological reforms (e.g., preregistration, replication). Yet, where knowledge is lacking, overemphasizing the problems that precipitate these reforms (e.g., p-hacking, HARKing) may lead students to de-value scientific methods as a credible means for generating knowledge. 
## OBJECTIVE: Understanding students’ naive conceptions about how science works and the norms that guide scientific best practice is important so that teachers can adapt their teaching to the students’ existing understandings. 
## METHOD: This study examined ### incoming undergraduate psychology students’ understandings of how research *should* be conducted (norms) and how they believed research *is* conducted (practice) using an online survey. 
## RESULTS: We found that XXX. . .
## CONCLUSION:

Keywords: open science, psychology, teaching, reproducibility, replication
wordcount: X

bibliography: ['r-references.bib','Undergrads & Open Science (public).bib']
floatsintext: yes
figurelist: no
tablelist: no
footnotelist: no
linenumbers: yes
mask: yes
draft: no
documentclass: apa6
classoption: man
affiliation:
- id: '1'
  institution: Swinburne University of Technology
- id: '2'
  institution: Massey University
---
<!-- I've only partially entered authorship deets for the moment and set it to mask authorship info when knitting
It's set to default to knit to .docx, but can also knit to pdf (if you have a tex distro installed)
The pdf looks nicer and might be good for a preprint but .docx probably easiest to use for journal submissions.
To knit to RMarkdown you will probably need the papaja package installed, and to knit to .pdf you will need a tex distro (e.g., TinyTex).
However, it is possible to run all the R code (without knitting to .docx or .pdf) by clicking Run > Run All Chunks Below.
This could be useful in future for readers interested in reproducing results but who don't have or wish to install 
papaja and its many dependencies.
-->

@@

```{r setup, include = FALSE}
library(papaja)
library(here)
library(tidyverse)
library(finalfit) # to keep trailing zeros & round_tidy
library(psych) #for correlation matrices
library(tidyselect) 
library(psychometric) # for correlation confidence intervals - might not need...
library(broom)

@@

The last decade has seen unprecedented change in methodological and reporting practices in psychology. These changes were partly precipitated by what is popularly known as the "replication crisis": The discovery that close replications of published psychological studies are often unable to replicate the original findings [@kleinInvestigatingVariationReplicability2014; @kleinManyLabsInvestigating2018]. These apparent problems with replication have lead to a variety of potential solutions to make research practices more reproducible and transparent, including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@simmons21WordSolution2012], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018]. These calls for more reproducible and transparent research practices prompted the discipline to reflect on the norms and beliefs that underpin its practice of research. Many studies have polled researchers' understandings of and adherence to open science norms, beliefs, and practices [e.g., @baker500ScientistsLift2016; @openscienceworkinggroup2017SurveyOpen2018; @harrisUseReproducibleResearch2018].

The most comprehensive set of principles for how science *ought* to be practiced are Merton's norms of science [@mertonNoteScienceDemocracy1942]. Scientists [@andersonExtendingMertonianNorms2010] and graduate students [@andersonGraduateStudentExperience1994] alike have historically endorsed the normative value of Merton's principles. Furthermore, many of the recent practices designed to make science more transparent and open reflect Mertonian norms [see @vazireWeWantBe; vazireWhereAreSelfcorrecting2020]. For example, the practice of sharing open source software corresponds to the Mertonian norm of *communism*: Scientists should have common ownership of scientific goods. Similarly, the practices of sharing of preprints for open peer review and open data for checking of reproducibility corresponds to the norm of communality, and also to that of *organised skepticism*: Scientific claims should be subjected to critical scrutiny. Preregistration can be connected to the norm of *disinterestedness*: By making (and preregistering) decisions about how to analyse data before results are produced, a researcher can limit the degree to which the substantive results produced by different analytic strategies affect their decisions regarding which analyses to report. In this sense, the ongoing reform in psychological research can partly be understood as simultaneously a set of new practices and a re-affirmation of established norms.

Rapid changes in methodological practice and empirical findings present significant pedagogical challenges for the teacher of psychology. Keeping textbooks and other instructional materials up to date is difficult when supposedly well-established findings are contradicted by new replications emerging at a rapid pace. Furthermore, training in emerging methodological practices is crucial for graduate students who may go on to apply psychological research methods themselves. Even for students who do not go on to conduct research themselves, an understanding of contemporary methodological practices - and problems with methodological practices in psychology - is essential for becoming informed and critical consumers of psychological knowledge. Studies have therefore begun to explore strategies for educating psychology students about replicability and open science practices [e.g., @chopikHowWhetherTeach2018; @graheHarnessingUndiscoveredResource2012; @jekelHowTeachOpen2020; @schonbrodtTrainingStudentsOpen2019]. These initiatives may help ingrain open science norms and change attitudes about research practices, but we know little about what these students know or believe about open science research practices prior to entering the university classroom. There are several reasons why this knowledge could be useful.

First, unlike some psychological phenomena in undergraduate courses (e.g., models of working memory, or the internal workings of human senses), the replication crisis is frequently discussed in mainstream and social media [e.g., @ogradyPsychologyReplicationCrisis2020; @yongPsychologyReplicationCrisis2016; @yongPsychologyReplicationCrisis2018]. Students may plausibly have some knowledge about these issues obtained prior to (or independently of) their formal studies. Teaching methods should thus be informed by some understanding of what students' pre-existing levels of knowledge are.

Second, when psychology students are beginning their university studies, they are often learning for the first time about how and why it is useful to apply scientific methods to studying human behaviour (rather than only relying on alternative sources of knowledge such as intuition or anecdote or authority). An emphasis on problems with replicability could at least in principle leave these students unconvinced that scientific methods for studying human behaviour are valuable *at all*, leaving them to favour even less credible alternative sources of knowledge. For instance, @chopikHowWhetherTeach2018 found that undergraduate students tended to trust the results of psychological studies *less* after a one-hour educational lecture about the replication crisis. This said, the effect of the lecture on trust of psychological studies was relatively small (d = -.36), and mean trust levels remained fairly high after the lecture (M = 4.94 on a scale of 1 to 7). Knowledge about incoming students’ “baseline” perceptions of the replicability of psychological science could further inform teachers about the salience of this risk.

Third, anecdotal evidence suggests that some students being taught about open science practices and reforms to improve reproducibility (such as open sharing of data and analysis code) are often surprised that these are not *already* standard practice [e.g. see tweets on this topic: @buraktuncaUygunTuncRmounce2021; @duyguuygun-tuncLastNightWas2021]. This could imply a need for educators to reinforce and build on students “naive” impressions rather than radically altering their understanding of how science should be done. On the other hand, other evidence suggests that undergraduate students may quickly begin to engage in practices that hamper reproducibility. For example, @moranKnowItBad2021 found that 26.5% of the undergraduate students in their Canadian sample admitted “Conducting multiple statistical analyses on the same dataset in an attempt to find a statistically significant result” (i.e., p-hacking), while 9.6% reported rounding down p-values. The extent to which incoming psychology students may - or may not - typically be “naive open scientists” is useful knowledge for guiding pedagogical approaches.

For these reasons, we aimed to conduct a study describing what incoming undergraduate students of psychology believe about reproducibility and open science practices in psychology. Our survey encompassed questions norms (how students felt research *should* be conducted), norms in practice (how students believe psychological research *is* conducted) and replicability (how replicable students believe psychological research is). In doing so we hope to provide knowledge which can inform the pedagogy of teaching about replication and open science practices. This study is exploratory [see @wagenmakersAgendaPurelyConfirmatory2012] and descriptive, and does not involve the specification or testing of hypotheses.

@@

Of the remaining `r n` participants, most reported being
18-24 years old (*n* = `r age[1,2]`), `r age [2,2]` 
reported that they were 25-34 years old, `r age [3,2]` were 35-44 years old,
`r age [4,2]` were 45-54 years old, and `r age [5,2]` was 55-64 years old.

The majority of participants (*n* = `r gender[1,2]`) reported that they were female, 
`r gender[2,2]` reported that they were male, `r gender[3,2]` participants reported 
their gender identity as "queer man", and `r gender[3,2]` participants reported 
non-binary gender.^[While the response "queer man" could potentially be coded as
"male", we are aware that some individuals who report gender in this way would
not feel that such reclassification was appropriate. We have retained the original
response in order to provide a faithful representation of the participant's 
self-reported gender.]

Most participants reported attending university in Australia (*n* = `r uni_country[1,2]`), 
the United Kingdom (*n* = `r uni_country[5,2]`), or New Zealand (*n* = `r uni_country[4,2]`). Nearly all reported graduating from high
school or secondary school (*n* = `r hs_status[3,2]`). Of those participants who 
attended high school, fewer than half completed psychology courses in 
high school (*n* = `r hs_psyc[2,2]`). Most reported their nationality as being from Australia (*n* = `r nationality[3,2]`), the United Kingdom (*n* = `r nationality[24,2]`), or China
(*n* = `r nationality[6,2]`). About 2/3rds of participants reported that at least one of their parents attended university (*n* = `r first_gen[2,2]`).

```{r qual responses}

# [breadcrumbs] 
 # once qual responses are coded, I will need to return here to 
 # include details about which univrsity the participant is enrolled in
 # name of qualification
 # major [how many are majoring in psyc; NAs; will decide later?]

@@

Our approach to measuring norms and counternorms focussed on participants' evaluation of ten specific open science practices that reflected diverse open science norms rather than trying to measure endorsement of the more abstract Mertonian norms (cf. Anderson et al., 2007). <!-- Mention here our discussions workshopping of common open science norms at SIPs? ! -->
The practices assessed in our survey included: critical thinking, preregistration, registered reports, p-hacking, hypothesising after the results are known (HARKing), providing sufficient information of replicability, preprints, open materials, open data, and open access publishing. Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." Although we acknowledge the existence of important debate about the merits of some of these practices [e.g., @TQMP16-4-376, @rubinWhenDoesHARKing2017, @szollosiPreregistrationWorthwhile2020], we selected the items to be emblematic of common concerns in the open science movement.

There were 20 scenarios in total (see Table \@ref(tab:norm_counternorm_items)). Participants rated their agreement with each prescriptive statement on a 1 (strongly disagree) to 5 (strongly agree) scale.

@@

We also sought to measure participants' normative beliefs about how psychological science was actually conducted by researchers around the world. To that end we asked participants, "When you consider all of the psychology studies conducted globally each year, what percentage of them would have the following characteristics?" These practices corresponded approximately to the ten norm-counternorm pairs described above, albeit with one norm excluded on the basis of not referring to externally observable behaviour (critically evaluating published studies vs. accepting them), and one practice added out of interest (data sharing on request).  (see Table XX). Participants were given a slider bar ranging from 0% to 100% to record their estimate.

@@

In line with our preregistered analysis plan, we calculated the difference in means
between responses to each norm item and its accompanying counternorm, along with 
95% confidence intervals. For this analysis, we removed three cases with missing values. 
Table XX displays the means and standard deviations for each norm, counternorm, 
and the difference values.

@@

In general, the students seemed to endorse open science practices: For seven of the ten open science practices, agreement with the norm item was stronger than for the corresponding counternorm. However, the extent to which participants endorsed open science norms varied very substantially across different practices. Participants most strongly endorsed norms that researchers should provide sufficient information about studies to permit replicability, be critical of published findings, and avoid p-hacking (means > 4; 4 representing 'agree'). They also tended to agree that researchers should avoid HARKing, share papers as open access, share open materials, and preregister their studies; the means for these items were all between 3.5 and 4. On the other hand, they tended to disagree with the practice of sharing preprints prior to peer review and, to a lesser extent, with sharing open data. The practice of registered reports was the one about which participants were most equivocal, with very similar levels of agreement (near the midpoint of 3) with both norm and counternorm for this item. This may be relatively unsurprising, given that the registered reports are perhaps the most recent innovation in the list of practices.

Unsurprisingly, there were substantial negative correlations between most norm and counternorm pairs, with the exception of the norm and counternorm items relating to preregistrations and HARKing.

@@

# clean up the tibble                          
practice_means_corr <- practice_means_corr %>% 
  mutate(Practice = practice) %>% 
  dplyr::select(-c(practice,estimate, conf.low, conf.high)) %>% 
  relocate (Practice, .before = Norm) %>% 
  relocate (p.value, .after = last_col())

# breadcrumbs: keep the values that I need from this tibble
# use p_tidy? to clean up the pvalues {done!}
# round the corr & CI {done!}
# join with the practice_means tibble & turn into a table {done!}
# need to figure out whether I can rotate a page in papaja

# just keeping this here for now, but will be able to delete
# critical_corr <- round(cor(df$critical_norm, df$critical_cnorm),2)
# critical_CI <- round(CIr(r = critical_corr, n = nrow(df), level = 0.95),2)
# 
# hark_corr <- round(cor(df$hark_norm, df$hark_cnorm),2)
# hark_CI <- round(CIr(r = hark_corr, n = nrow(df), level = 0.95),2)
# 
# info_for_rep_corr <- round(cor(df$info_for_rep_norm, df$info_for_rep_cnorm),2)
# info_for_rep_CI <- round(CIr(r = info_for_rep_corr, n = nrow(df), level = 0.95),2)
# 
# open_access_corr <- round(cor(df$open_access_norm, df$open_access_cnorm),2)
# open_access_CI <- round(CIr(r = open_access_corr, n = nrow(df), level = 0.95),2)
# 
# open_data_corr <- round(cor(df$open_data_norm, df$open_data_cnorm),2)
# open_data_CI <- round(CIr(r = open_data_corr, n = nrow(df), level = 0.95),2)
# 
# open_materials_corr <- round(cor(df$open_materials_norm, df$open_materials_cnorm),2)
# open_materials_CI <- round(CIr(r = open_materials_corr, n = nrow(df), level = 0.95),2)
# 
# phack_corr <- round(cor(df$phack_norm, df$phack_cnorm),2)
# phack_CI <- round(CIr(r = phack_corr, n = nrow(df), level = 0.95),2)
# 
# preprint_corr <- round(cor(df$preprint_norm, df$preprint_cnorm),2)
# preprint_CI <- round(CIr(r = preprint_corr, n = nrow(df), level = 0.95),2)
# 
# prereg_corr <- round(cor(df$prereg_norm, df$prereg_cnorm),2)
# prereg_CI <- round(CIr(r = prereg_corr, n = nrow(df), level = 0.95),2)

# breadcrumbs: 
# I need to use apa_tables.... (in line with papaja)
# pull means & sd into the same column with (sd) in parentheses [done!]
# headings should then be norm, counternorm, difference [done!]
# add correlations with 95% CIs 
# update practice descriptions so they make sense to readers

@@

```{r correlation_matrix}
#pairs.panel etc. won't really work because there are too many variables
#And we only need corrs between matched pairs
#So doing this a bit more manually
layout(matrix(1:8, ncol = 4))

plot(df$critical_norm ~ jitter(df$critical_cnorm), xlab = "critical counternorm", ylab = "critical norm")
abline(lm(df$critical_norm ~ df$critical_cnorm), col = "blue")
legend(x='bottomright', legend=paste('Cor =', round(cor(df$critical_norm, df$critical_cnorm),2)))

plot(df$prereg_norm ~ jitter(df$prereg_cnorm), ylab = "Prereg norm", xlab = "Prereg counternorm")
abline(lm(df$prereg_norm ~ df$prereg_cnorm), col = "blue")
legend(x='bottomright', legend=paste('Cor =', round(cor(df$prereg_norm, df$prereg_cnorm),2)))

plot(df$reg_report_norm ~ jitter(df$reg_report_cnorm), ylab = "Reg Reports norm", xlab = "Reg Reports counternorm")
abline(lm(df$reg_report_norm ~ df$reg_report_cnorm), col = "blue")
legend(x='bottomleft', legend=paste('Cor =', round(cor(df$reg_report_norm, df$reg_report_cnorm),2)))

plot(df$phack_norm ~ jitter(df$phack_cnorm), ylab = "p-hacking rnorm", xlab = "p-hacking counternorm")
#potential confusion here about direction of phrasing (pro p-hacking = counternorm?)
abline(lm(df$phack_norm ~ df$phack_cnorm), col = "blue")
legend(x='bottomleft', legend=paste('Cor =', round(cor(df$phack_cnorm, df$phack_norm),2)))

plot(df$hark_norm ~ jitter(df$hark_cnorm), ylab = "HARKing norm", xlab = "HARKing counternorm")
abline(lm(df$hark_norm ~ df$hark_cnorm), col = "blue")
legend(x='bottomright', legend=paste('Cor =', round(cor(df$hark_cnorm, df$hark_norm),2)))

plot(df$info_for_rep_norm ~ jitter(df$info_for_rep_cnorm), ylab = "Replicability norm", xlab = "Replicability counternorm")
abline(lm(df$info_for_rep_norm ~ df$info_for_rep_cnorm), col = "blue")
legend(x='right', legend=paste('Cor =', round(cor(df$info_for_rep_norm, df$info_for_rep_cnorm),2)))

plot(df$preprint_norm ~ jitter(df$preprint_cnorm), ylab = "Preprints norm", xlab = "Preprints counternorm")
abline(lm(df$preprint_norm ~ df$preprint_cnorm), col = "blue")
legend(x='bottomleft', legend=paste('Cor =', round(cor(df$preprint_norm, df$preprint_cnorm,
                                                       use = "pairwise.complete.obs"),2)))
